Formal Analysis of EDHOC Key Establishment for Constrained IoT Devices

### 2022-07-20 protocol.tex
[fix] separate the non-formal aspects of TEEs into their own section

>>>>

%------------------------------------------------------------------------- sec
\section{Implementation Aspects and Key Protection}
\label{sec:TEE}
Adversaries may have physical access to implementations, this is perhaps an
even higher risk in an unsupervised IoT setting.
%
Implementations can make use of Trusted Execution Environments (TEE) hardened
against physical attacks to mitigate adversaries with physical access to the
cryptographic keys.
%

TEEs come in various forms of differing complexity.
%
Some, like ARM Trust Zone and Intel SGX are general purpose execution
environments, which are flexibly programmable.
%
Other, like the Universal Subscriber Identity Modules (USIM) used for
authentication to 3GPP mobile networks, have application specific interfaces for
authentication and key agreement protocols etc.
%
A key aspect is how much of the application is placed in the TEE and how much is
outside.
%

For larger devices that include general purpose processors with Trust Zone or
SGX, entire \mEdhoc{} and \mOscore{} may reside inside the TEE.
%
For constrained IoT devices in the lower end of the scale, a TEE may have to be
implemented using a special-purpose integrated circuit.
%
In the latter case, it may be beneficial to follow a minimalistic approach, and
contain the long-term key and only
the operations that need access to it in the TEE for cost reasons.
%

It may at first appear more secure to implement as much as possible inside the
TEE, but there is a security trade-off: the more code inside the TEE,
the higher the risk of implementation errors in the security-critical code.
%
Because the security critical code runs in the area where the long-term keys
reside, an implementation error here risks leaking information of the key to the
adversary.
%
From this perspective, it may be beneficial to follow the minimalistic approach
even when having access to Trust Zone or SGX.
%

A slightly more secure division of functionality is to also keep the
session key inside
the TEE and extend the interface to accept messages and return the
(en/de)crypted counter part.
%
That is, the interface exposes \mAead{} functions in the interface.
%
